\documentclass[a4paper, 8pt]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=0.4in, right=0.4in, top=0.3in, bottom=0.2in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}

% --- DOCUMENT SETUP ---
\definecolor{linkblue}{HTML}{0000EE}
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
    pdfborder = {0 0 0},
}

% --- LAYOUT CUSTOMIZATION ---
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\titleformat{\section}
  {\Large\scshape\raggedright}
  {}
  {0em}
  {}
  [\titlerule]
\titlespacing*{\section}{0pt}{4pt}{4pt}

\setlist[itemize]{
    leftmargin=*, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt
}

% --- DOCUMENT START ---
\begin{document}

% --- HEADER: PERSONAL DATA ---
\begin{center}
    {\Huge\textbf{Huma Naaz Mohammad}}\\
    
    \vspace{2pt}
    +91 8793955356 ~|~ 
    \href{mailto:humanaaz.mohammad@gmail.com}{humanaaz.mohammad@gmail.com} ~|~ 
    \href{https://www.linkedin.com/in/huma-naaz-mohammad-8a6251296/}{LinkedIn} ~|~ 
    \href{https://github.com/naazie}{GitHub} ~|~ 
    \href{https://leetcode.com/humanaaz/}{LeetCode}
\end{center}

% --- EDUCATION (Updated with Minor) ---
\section*{Education}
\textbf{Walchand College of Engineering, Sangli} \hfill \textbf{2023 --- 2027} \\
\textit{B. Tech. in Computer Science (Minor in Fintech)} \hfill \textit{CGPA: 9.12 / 10}

\textbf{Arihant College of Arts, Commerce and Science, Pune} \hfill \textbf{2021 --- 2023} \\
\textit{Junior College (11th and 12th)} \hfill \textit{Percentage: 83.3\%}

\textbf{Bishops Co-Ed School, Kalyani Nagar, Pune} \hfill \textbf{2008 --- 2021} \\
\textit{Schooling - ICSE Board} \hfill \textit{Percentage: 95.1\%}

% --- EXPERIENCE (Updated with Impact) ---
\section*{Work Experience}
\textbf{AptTech} - Internship \hfill \textbf{Summer 2025}
\begin{itemize}
    \item Designed and built a full-stack web application connecting students with mentors and teachers within the institute.
    \item Developed a responsive user interface using Next.js and Tailwind CSS with secure authentication and real-time data handling via Firebase.
\end{itemize}

% --- PROJECTS (Updated with Impact) ---
\section*{Projects}
\textbf{Real-Time Messaging Platform} \hfill \href{https://github.com/naazie/TheHumanDiscord}{GitHub}\\
\textit{MERN, Socket.io}
\begin{itemize}
    \item Architected a real-time messaging system using WebSockets (Socket.IO) with multi-client synchronization and persistent storage.
    \item Designed server/channel-based communication architecture with JWT authentication and protected REST APIs.
    \item Implemented global socket lifecycle management in React to prevent duplicate connections and render-loop issues.
\end{itemize}
\vspace{2pt}

\textbf{Latent Semantic Analysis–Based Document Clustering} \hfill \href{https://github.com/naazie/ML-ISE2-Final}{GitHub}
\begin{itemize}
    \item Developed an Latent Semantic Analysis(LSA) pipeline using Singular Value Decomposition(SVD) to transform raw text into dense embeddings for unsupervised topic discovery.
    \item Built semantic similarity networks using Cosine Similarity to automate document clustering.
\end{itemize}
\vspace{2pt}

\textbf{AI-Powered Laptop Recommendation Website - SmartSelect: Tech, Chosen Right} \hfill 
\href{https://github.com/naazie/SmartSelect-AI-Powered-Laptop-Recommendation}{GitHub}\\
\textit{ReactJS, Python }
\begin{itemize}
    \item An LLM-API powered web application for personalized laptop recommendations based on user needs and budget.
    \item Implemented sentiment analysis and keyword extraction on real user reviews to provide transparent pros, cons, and feature comparisons.
\end{itemize}

% --- TECHNICAL SKILLS (Updated and Reorganized) ---
\section*{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
    \textbf{Languages}    & C++, Python\\
    \textbf{Web Tech}      & HTML, CSS, JavaScript, React, MongoDB, SQL\\
    \textbf{Core CS}      & Data Structures \& Algorithms, OOP, OS, DBMS \\
    \textbf{ML}           & Regression, Classification, Clustering, Feature Engineering, Cross-Validation, Hyperparameter Tuning.\\
    \textbf{Developer Tools} & Git, Linux, Docker/Kubernetes \\
    \textbf{Fintech Coursework} & {Introduction to Financial Markets, Risk Management and Compliance} 
\end{tabularx}

% --- EXPERIENCE (Updated with Impact) ---
\section*{Experience}
\textbf{WLUG (Walchand Linux Users' Group)} \hfill \textbf{2023 --- Present}
\begin{itemize}
    \item Joined as an active member, conducted 3 annual Linux workshops, and led open-source community discussions.
    \item Served as Assistant Club Service Director (2024–2025); presented in The Linux Vault (100+ participants) and volunteered in Open Source Day, Linux Diary, and Metamorphosis 2k24.
    \item Currently serving as the main designer (May 2025–Present); leading visual design for club events, and volunteered in LinuxDiary 6.0.
\end{itemize}

\textbf{WCE ACSES (Association of Computer Science and Engineering Students)} \hfill \textbf{2023 --- 2025}
\begin{itemize}
    \item Appointed Assistant Secretary (2024–2025)
     \item Authored and delivered technical presentations on C++ and OOP principles to audiences of more than 200 students, fostering community engagement and simplifying complex topics.
\end{itemize}

% --- ACHIEVEMENTS ---
\section*{Achievements}
\begin{itemize}
    \item \textbf{2nd Runner-up}, MongoDB workshop by ACM Student Chapter \hfill \textit{Jan 2025}
    \item \textbf{Published Research Paper}: "Plastic Waste Management: Awareness and Recycling for Environmental Justice" \hfill \textit{Jan 2025}
    \item \textbf{Finalist}, Standout by Personality Advancement Circle of Engineers, WCE (180+ participants) \hfill \textit{Aug 2023}
\end{itemize}

\end{document}
